---
title: "Farris_KPI_Analysis"
format: html
editor: visual
---

```{r message = FALSE}
library(dplyr)
library(ggplot2)
library(corrplot)
library(caret)
library(randomForest)
library(knitr)
```

```{r}
transfers <- read.csv('final_transfer_renamed.csv')

```

## Convert Data to Per 90 Variables

```{r}
transfers90 <- transfers %>%
  mutate(across(
          -c(player, age, season, transfer, nation, team, comp, matches_played, 
          minutes, minutes_by_90, matches_played_starter, matches_played_sub, matches_no_play,
          Total_Cmp.,Progressive_Passes_Received, TakeOn_Success_Percentage,
          TakeOn_Tackled_Percentage, Challenges_Tackle_Percentage, Aerial_Win_Percentage,
          Position),
          ~./minutes_by_90))
```

## Column Adjustment

Removed Columns: X, nation, team, comp, minutes, minutes_by_90, Position

Added: Binary Columns for each Position \~

1.  FW: Forward
2.  MF: Mid Fielder
3.  DF: Defender

```{r}
## ANDREW ###
transfers90 <- transfers90 %>%
  select(-c(X, nation, team, comp, minutes, minutes_by_90)) %>%
  mutate(MF = ifelse(grepl("MF", Position), 1,0),
         FW = ifelse(grepl("FW", Position), 1,0),
         DF = ifelse(grepl("DF", Position), 1,0)) %>%
  select(-Position)
```

## Row Adjustment

Removed NA values

```{r}
transfers90 %>%
  filter(is.na(Challenges_Tackle_Percentage))
```

```{r}
transfers90 <- transfers90 %>%
  na.omit() 
```

# Recursive Feature Selection

```{r}
X <- transfers90 %>%
  select(-c(player, season, transfer))

y <- as.factor(transfers90$transfer)

```

## Bootstrap Method

```{r}
control <- rfeControl(
  functions = rfFuncs,  
  method = "boot",        
  number = 5)
```

```{r rfe_analysis, cache = TRUE}
rfe_result <- rfe(
  x = as.data.frame(X),
  y = y,
  sizes = c(10,20,30,40,50), 
  rfeControl = control,
  metric = 'Kappa',
  strata = y
)
```

```{r}
variables <- rfe_result$results$Variables
kappa <- rfe_result$results$Kappa

ggplot() +
  geom_point(aes(x = variables, y = kappa)) +
  theme_minimal() +
  ylab("Kappa") +
  xlab("Number of Variables") +
  ggtitle("Variable Selection - Bootstrap")
  
```

```{r}
kable(rfe_result$results)
```

```{r}
top_vars <- predictors(rfe_result)

kable(top_vars)
```

## Cross Validation Method

```{r}
control <- rfeControl(
  functions = rfFuncs,  
  method = 'cv',        
  number = 5)
```

```{r rfe_analysis2, cache = TRUE}
rfe_result <- rfe(
  x = as.data.frame(X),
  y = y,
  sizes = c(10,20,30,40,50), 
  rfeControl = control,
  metric = 'Kappa',
  strata = y
)
```

```{r}
variables <- rfe_result$results$Variables
kappa <- rfe_result$results$Kappa

ggplot() +
  geom_point(aes(x = variables, y = kappa)) +
  theme_minimal() +
  ylab("Kappa") +
  xlab("Number of Variables") +
  ggtitle("Variable Selection - Cross Validation")
  
```

```{r}
kable(rfe_result$results)
```

```{r}
top_vars <- predictors(rfe_result)

kable(top_vars)
```

## Interaction Exploration

Forward

-   Raw Goals and Assists

-   Shot Creating Action

-   Progressive Passes Received

-   Shots Leading to Another Shot

Midfield

-   Passes Leading to Shot

-   Passes in Final Third of Pitch

-   Progressive Passes

-   Tackles Total

Defender

-   Defensive Actions Leading to Shot

-   Blocked Shots

-   Blocked Passes

-   Tackles + Interceptions

-   Clearances
